### 2014-06-06 evaluation.tex
region stats and gradient explanation + figure
ergion selection and some more eval setup

\begin{description}
  \item[Original] \hfill \\
  The original order of the
  \item[Second] \hfill \\
  The second item
  \item[Third] \hfill \\
  The third etc \ldots
\end{description}

\begin{figure}
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
    \caption{Distribution of number of regions per image.}\label{fig:roi_hist}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.46\linewidth}
    % \includegraphics[width=\linewidth]{PLACEHOLDER}
    \rule{5cm}{4cm}
    \caption{\todo{Another small figure here}}\label{fig:PLACEHOLDER}
\end{subfigure}
\caption{}
\end{figure}

>>>>

\begin{description}
  \item[Original] \hfill \\
  The original order of the Selective Search regions of interest.
  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.
  \item[Random] \hfill \\
  A completely blind permutation of the original order.
  \item[Region Selection] \hfill \\
  The order is determined as described in \autoref{sec:dynamic}.
  The region statistics feature from \autoref{sec:region} is always used, allowing learning an effective ordering.
  Additionally, we consider the Pixel Gradient and the Pyramid-R-CNN features.
\end{description}

\begin{figure}
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
    \caption{Distribution of number of regions per image.}\label{fig:roi_hist}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.46\linewidth}
    \includegraphics[width=\linewidth]{figures/gradient.pdf}
    \caption{Example of the CNN gradient.}\label{fig:gradient}
\end{subfigure}
\caption{}
\end{figure}

### 2014-06-06 method.tex
ergion selection and some more eval setup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dynamic region selection}\label{sec:dynamic}

\autoref{fig:combined} shows the dynamic region selection loop.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \todo{Explain dynamic selection of region batches.}
\item
  \todo{Explain iterative training procedure.}
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Region selection}\label{sec:dynamic}

As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
Unlike the Cascade-CNN, this process of region selection does not reject regions flat out, but merely reorders them to be processed later.

We consider two ways of selecting regions by their score.
The first is to simply sort the regions by score, and to take batches in that sorted order
We quickly discovered that this naive method does not result in good performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesized that this is because the highest scoring regions may all

\subsubsection{Dynamic feature update}
